Cognitive and Auditory Predictors of Dysarthric Speech Understanding in Older

### 2024-12-13 Manuscript Analyses/manuscript_analysis.Rmd

demo <- demo %>%
  dplyr::filter(id != 323 & id != 332 )

@@

A total of 58 older adult listeners participated in the study (excluding the two listeners we had to remove). The overall demographic information for the 58 participants are in the table below.

>>>>

demo <- demo %>%
  dplyr::filter(id != 323 & id != 332)

@@

A total of 58 older adult listeners participated in the study. The overall demographic information for the participants are in the table below.
